Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-04-01 fmics/paper.tex
try to keep figs 6 and 7 on the same page
minor revision sec 4

\begin{figure}[t]
\begin{tabular}{ll}
$\;\mathsf{tap}\;0\;0=0\quad\quad$ & $\mathsf{tap}\;0\;x=0$\\
$\;\mathsf{tap}\;1\;0=1-1\quad$ &  $\mathsf{tap}\;1\;x=2-1$\\
$\;\mathsf{tap}\;2\;0=8-1\quad$ &  $\mathsf{tap}\;2\;x=16-1$\\
$\;\dots\quad$ & $\mathsf{tap}\;6\;x=128-1\quad\text{(where each $x>0$)}$\\[1ex]

@@

\begin{figure}[t]
\begin{tabular}{l}
$\mathsf{delay\_sum}\;0=0$\\
$\mathsf{delay\_sum}\;n=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\quad\text{where $(n',\_)=\mathsf{input}\;n$}$\\[1ex]

@@

The proof of Theorem~\ref{max_error} is straightforward when summarized, as above.
However, as for all of our theorems, there are several non-trivial details underlying the high-level summary provided.
For example, \emph{proving} that the maximum difference between the end terms in a sum is the maximum difference between consecutive elements multiplied by the number of terms requires an inductive argument.
Our HOL4 proof script for verification of SRS consists of 750 lines of code.
We proved 69 theorems, including 14 definitions.
In addition, we had to prove approximately 30 generic theorems that were added to HOL4 libraries during this work.

>>>>

\begin{figure}[p]
\begin{tabular}{ll}
$\;\mathsf{tap}\;0\;0=0\quad\quad$ & $\mathsf{tap}\;0\;x=0$\\
$\;\mathsf{tap}\;1\;0=1-1\quad$ &  $\mathsf{tap}\;1\;x=2-1$\\
$\;\mathsf{tap}\;2\;0=8-1\quad$ &  $\mathsf{tap}\;2\;x=16-1$\\
$\;\dots\quad$ & $\mathsf{tap}\;6\;x=128-1\quad\text{(where each $x>0$)}$\\[1ex]

@@

\begin{figure}[p]
\begin{tabular}{l}
$\mathsf{delay\_sum}\;0=0$\\
$\mathsf{delay\_sum}\;n=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\quad\text{where $(n',\_)=\mathsf{input}\;n$}$\\[1ex]

@@

The proof of Theorem~\ref{max_error} is straightforward when summarized, as above.
However, as for all of our theorems, there are several non-trivial details underlying the high-level summary provided.
For example, \emph{proving} that the maximum difference between the end terms in a sum is the maximum difference between consecutive terms multiplied by the number of terms requires an inductive argument.
Our HOL4 proof script for verification of SRS consists of 750 lines of code.
We proved 69 theorems, including 14 definitions.
In addition, we had to prove approximately 30 generic theorems that were added to HOL4 libraries during this work.
